---
title: "Exploration"
author: "Pedro Gaxiola"
date: "2023-02-03"
output:
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages used

```{r}
library(tidyverse)
library(lemon)
knit_print.data.frame <- lemon_print
```


## Reading in the data

The original test data will be named test_data and the original train data will be train_data.\newline 
The data is in the csv format.

```{r}
test_data <- read.csv("house-prices-advanced-regression-techniques/test.csv")
train_data <- read.csv("house-prices-advanced-regression-techniques/train.csv")
```

## Creating data frames for the original data

The data frames df_train and df_test are the data frames of the original loaded data

```{r}
df_test <- data.frame(test_data)
df_train <- data.frame(train_data)
```

## Initial description of the data
The test csv file contains 1459 rows and 80 columns. \newline
The train csv file contains 1460 rows an 81 columns. \newline



```{r}
dim(df_test)
dim(df_train)
```

## Data types
These are the names and data types df_train.

```{r, render=lemon_print, caption= "Variables for df_train"}
a1 <- tibble(variable = names(df_train), data_type = sapply(df_train, class)) %>% slice(1:27)
a2 <- tibble(variable = names(df_train), data_type = sapply(df_train, class)) %>% slice(28:54)
a3 <- tibble(variable = names(df_train), data_type = sapply(df_train, class)) %>% slice(55:81)
cbind(a1, a2, a3)
rm(a1)
rm(a2)
rm(a3)
```

## Duplicate entries

It seems that the data does not contain any duplicate entries.
```{r}
sum(duplicated(df_train))
sum(duplicated(df_test))
```


## Missing Values
The training data contains a total of 6965 missing values. \newline
The testing data containes a total of 7000 missing values. 

```{r}
sum(is.na(df_train))
sum(is.na(df_test))
```

The missing values for each variable are shown below. \newline
The percent of missing values for each column is also shown. \newline
If a variable is not listed, then it should not have any missing values. \newline
The entries NA were added to make the tables align correctly and do not represent anything. 


```{r, render= lemon_print, caption= "Missing Values for df_train"}
a4 <- tibble(variable = names(df_train),
       missing_value = colSums(is.na(df_train)),
       percent_missing =colSums(is.na(df_train))/nrow(df_train) *100
       ) %>%
  filter(missing_value > 0)
cbind(slice(a4, 1:10), rbind(slice(a4, 11:19), c(NA, NA, NA)))
```


```{r, render= lemon_print, caption= "Missing Values for df_test"}
a5 <- tibble(variable = names(df_test),
       missing_value = colSums(is.na(df_test)),
       percent_missing =colSums(is.na(df_test))/nrow(df_test) *100
       ) %>%
  filter(missing_value > 0) 

cbind(slice(a5, 1:17), rbind(slice(a5, 18:33), c(NA, NA, NA)))
```


```{r, render= lemon_print, caption= "Combined Missing Values for df_test and df_train"}
a6 <- rbind(df_test, select(df_train, -c("SalePrice")))

a6 <- tibble(variable = names(a6),
       missing_value = colSums(is.na(a6)),
       percent_missing =colSums(is.na(a6))/nrow(a6) *100
       ) %>%
  filter(missing_value > 0)
cbind(slice(a6, 1:17), slice(a6, 18:34))
```
















