---
title: "Exploration"
author: "Pedro Gaxiola"
date: "2023-02-03"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages used

```{r}
library(tidyverse)
```

## Reading in the data

The original test data will be named test_data and the original train data will be train_data. \newline The data is in the csv format.

```{r}
test_data <- read.csv("house-prices-advanced-regression-techniques/test.csv")
train_data <- read.csv("house-prices-advanced-regression-techniques/train.csv")
```

## Creating data frames for the original data

The dataframes df_train and df_test are the dataframes of the original loaded data

```{r}
df_test <- data.frame(test_data)
df_train <- data.frame(train_data)
```

## Initial description of the data
The test csv file contains 1459 rows and 80 columns. \newline
The train csv file contains 1460 rows an 81 columns. \newline


```{r}
dim(df_test)
dim(df_train)
```
These are the names of the variables in df_train.
```{r}
names(df_train)
```

The training data containes a total of 6965 missing values. \newline

```{r}
sum(is.na(df_train))
```

The missing values for each variable are shown below. The percent of missing values for each column is also shown.


```{r}
tibble(variable = names(df_train),
       missing_value = colSums(is.na(df_train)),
       percent_missing =colSums(is.na(df_train))/nrow(df_train) *100
       ) %>%
  filter(missing_value > 0)
```

```{r}

```




