---
title: "Exploration"
author: "Pedro Gaxiola"
date: "2023-02-03"
output:
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages used

```{r}
library(tidyverse)
library(lemon)
knit_print.data.frame <- lemon_print
```


## Reading in the data

The original test data will be named test_data and the original train data will be train_data. \newline The data is in the csv format.

```{r}
test_data <- read.csv("house-prices-advanced-regression-techniques/test.csv")
train_data <- read.csv("house-prices-advanced-regression-techniques/train.csv")
```

## Creating data frames for the original data

The dataframes df_train and df_test are the dataframes of the original loaded data

```{r}
df_test <- data.frame(test_data)
df_train <- data.frame(train_data)
```

## Initial description of the data
The test csv file contains 1459 rows and 80 columns. \newline
The train csv file contains 1460 rows an 81 columns. \newline



```{r}
dim(df_test)
dim(df_train)
```

These are the names and data types df_train.

```{r, render=lemon_print}
a1 <- tibble(variable = names(df_train), data_type = sapply(df_train, class)) %>% slice(1:27)
a2 <- tibble(variable = names(df_train), data_type = sapply(df_train, class)) %>% slice(28:54)
a3 <- tibble(variable = names(df_train), data_type = sapply(df_train, class)) %>% slice(55:81)
cbind(a1, a2, a3)
#my_data_types < cbind()
```


The training data contains a total of 6965 missing values. \newline

```{r}
sum(is.na(df_train))
```

The missing values for each variable are shown below. The percent of missing values for each column is also shown.


```{r, render=lemon_print}
tibble(missing_value = colSums(is.na(df_train)),
       percent_missing =colSums(is.na(df_train))/nrow(df_train) *100
       ) %>%
  filter(missing_value > 0)
```

```{r}

```




